
---
title: "Exploring the Palmer Penguins Dataset with R"
author: "Nanxuan Li"
date: "2026-09-26"
format: html
execute:
  echo: true
---



## Introduction

In this post, I will explore the Palmer Penguins dataset using R. I will compare the average body mass of different penguin species and create a simple bar chart.

My goal is to learn how to summarize and visualize data using R.



## Loading the Data

First, I will load the dataset and display the first six rows.

```{r}
#| warning: false

library(palmerpenguins)

head(penguins)
```

Data source: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/), Palmer Station Antarctica LTER.



## Comparing Species

Next, I will calculate the average body mass for each species.

```{r}
average_mass <- aggregate(
  body_mass_g ~ species,
  data = penguins,
  FUN = mean
)

average_mass
```



## Visualization

I will create a bar chart to compare the average body mass of the three penguin species.

```{r}
#| label: fig-r-penguin-mass
#| fig-cap: "Average body mass by penguin species."

barplot(
  average_mass$body_mass_g,
  names.arg = average_mass$species,
  ylab = "Average Body Mass (g)",
  xlab = "Species"
)
```



## Conclusion

The results show that Gentoo penguins have the highest average body mass among the three species. This analysis demonstrates how R can be used to summarize and visualize data.
